---
title: "Review Dashboard"
author: "Veronica Gosnell"
date: "2025-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include = FALSE}
library(viridis)
library(ggplot2)
library(marmap)
```

# Intro {.sidebar}

This dashboard covers several topics:

* The marmap package
* The viridis package
* Miscellaneous material

# Marmap Package

## Column 1

### Florida


<!-- data(florida) -->
<!-- autoplot(florida) -->


#errors with autoplot
#use this code instead:

```{r}
library(marmap)
library(ggplot2)
library(viridis)

# Load the bathymetry data
data(florida)

# Convert bathy object to data frame
florida_df <- as.xyz(florida)  # gives a data.frame with columns: x, y, z

# If as.xyz() returned columns Var1, Var2, value:
colnames(florida_df) <- c("x", "y", "z")

# Plot using ggplot2
ggplot(florida_df, aes(x = x, y = y, fill = z)) +
  geom_tile() +
  scale_fill_viridis(name = "Depth (m)", option = "C") +
  coord_fixed() +
  theme_minimal() +
  labs(
    title = "Bathymetry of Florida Region",
    x = "Longitude", y = "Latitude"
  )


```




The [marmap](https://cran.r-project.org/web/packages/marmap/index.html) package provides tools and data for visualizing the ocean floor. Here is an example contour plot of marmap's `florida` dataset.

## Column 2

### Hawaii


<!-- data(hawaii) -->
<!-- autoplot(hawaii) -->


#^ this code isn't working with autoplot
#use this code instead:

```{r}
library(marmap)
library(ggplot2)
library(viridis)

# Load the bathymetry data
data(hawaii)

# Convert bathy object to data frame
hawaii_df <- as.xyz(hawaii)

#rename columns manually
colnames(hawaii_df) <- c("x", "y", "z")

# Fix column names if needed
colnames(hawaii_df) <- c("x", "y", "z")  # x = long, y = lat, z = depth

# Plot using ggplot2
ggplot(hawaii_df, aes(x = x, y = y, fill = z)) +
  geom_tile() +
  scale_fill_viridis(name = "Depth (m)", option = "C") +
  coord_fixed() +
  theme_minimal() +
  labs(
    title = "Bathymetry around Hawaii",
    x = "Longitude", y = "Latitude"
  )

```



### Alaska


<!-- data(aleutians) -->
<!-- autoplot(aleutians) -->


#autoplot doesn't like me
#use this code instead:
```{r}
# Load the bathymetry data for Aleutians
data(aleutians)

# Convert bathy object to data frame
aleutians_df <- as.xyz(aleutians)

# Check column names to see if they need adjusting
head(aleutians_df)
str(aleutians_df)

# If column names are something like Var1, Var2, and value, rename them
colnames(aleutians_df) <- c("x", "y", "z")

# Plot using ggplot2
ggplot(aleutians_df, aes(x = x, y = y, fill = z)) +
  geom_tile() +
  scale_fill_viridis(name = "Depth (m)", option = "C") +
  coord_fixed() +
  theme_minimal() +
  labs(
    title = "Bathymetry of Aleutian Islands",
    x = "Longitude", y = "Latitude"
  )

```


# Viridis Package

## Column 1

### Viridis colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200))
```

### Magma colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "A"))
```

## Column 2

### Inferno colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "B"))
```

### Plasma colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "C"))
```

# Miscellaneous

## Column 1 {data-width=300}

### Bash support

```{bash}
ls *.Rmd
```

***

This chunk executes bash code.

### Python support

```{python}
x = 'hello, python world!'
print(x.split(' '))
```

***

This chunk executes python code.

## Column 2 {data-width=700}

### Tables with Kable 

```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(mtcars[1:5, ], caption = "A knitr kable.")
```

***

It is very easy to make tables with knitr's `kable` function.
