---
title: "Shiny Web App"
author: "Veronica Gosnell"
date: "2025-04-13"
output: html_document
runtime: shiny
---

The Shiny package builds interactive web apps powered by R. To call Shiny code from an R Markdown document, add runtime: shiny to the header

Use Shiny to run any R code that you like in response to user actions. Since web browsers cannot execute R code, Shiny interactions occur on the server side.


Htmlwidgets and Shiny elements rely on HTML and JavaScript. They will work in any R Markdown format that is viewed in a web browser, such as html documents, notebooks and websites, as well as dashboards and slide presentations.

If you include an interactive element in a static output format, like a PDF, R Markdown will embed a screenshot of the element.


```{r include = FALSE}
library(shiny)
library(viridis)
```

You've seen the Maunga Whau volcano displayed in a variety of colors. Now pick your favorite.

```{r echo = FALSE}
selectInput("colors", "Choose a color palette", 
  choices = c("viridis", "magma", "inferno", "plasma", "heat",
  "terrain", "topographic", "cyan/magenta", "rainbow"))

colorPalette <- reactive({
  switch(input$colors, 
         "viridis" = viridis(200),
         "magma" = viridis(200, option = "A"),
         "inferno" = viridis(200, option = "B"),
         "plasma" = viridis(200, option = "C"),
         "heat" = heat.colors(200),
         "terrain" = terrain.colors(200),
         "topographic" = topo.colors(200),
         "cyan/magenta" = cm.colors(200),
         "rainbow" = rainbow(200))
})

renderPlot({
  image(volcano, col = colorPalette())
})
```





