---
title: "Visualizing the ocean floor"
author: "Veronica Gosnell"
date: "2025-04-13"
output: html_document
params:
  data: "hawaii"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Visualizing the ocean floor"
output: html_document
params:
  data: "hawaii"
---

```{r include = FALSE}
install.packages('marmap')
library(marmap)
library(ggplot2)
```

The [marmap](https://cran.r-project.org/web/packages/marmap/index.html) package provides tools and data for visualizing the ocean floor. Here is an example contour plot of marmap's ``r params$data`` dataset.

```{r echo = FALSE}
data(list = params$data)
autoplot(get(params$data))
```

#error in this code ^

```{r}
# Install necessary packages (optional in final reports)
if (!requireNamespace("marmap", quietly = TRUE)) install.packages("marmap")
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")

library(marmap)
library(ggplot2)

# Load data from params
data(list = params$data)

# Get the bathy object
bathy_data <- get(params$data)

# Convert to data frame
bathy_df <- fortify(bathy_data)

# Plot using ggplot2
ggplot(bathy_df, aes(x = x, y = y, fill = z)) +
  geom_raster() +
  scale_fill_viridis_c() +
  coord_fixed() +
  theme_minimal()

```

#AI gave last chunk of code -> on hawaii data
#also added params:
#  data: hawaii
# to yaml


# add params argument to render to create a report that uses a new set of parameter values
# modified report to use the aleutians data set

render("5-parameters.Rmd", params = list(data = "aleutians"))


<!-- Parameters are useful when you want to re-render the same report with distinct values for various key inputs, for example: -->

<!-- Running a report specific to a department or geographic region. -->

<!-- Running a report that covers a specific period in time. -->

<!-- Running multiple versions of a report for distinct sets of core assumptions. -->

