---
title: "Some rmarkdown tips"
author: "Remko"
date: "12 September 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Inline code

We can put R code inline. For example, the mean of a set of 10 random numbers is `r mean(runif(10))`. 
Note that some rounding may be useful, like `r round(mean(runif(10)), 3)`.


# Tables

See the example doc on making tables. But here is a quick example, using the built-in mtcars dataset.

```{r}
library(knitr)
kable(mtcars[1:6,], caption="**Table 1.** The first 6 rows of the mtcars dataset")
```

We can even use that to format output of linear regression,

```{r}
fit <- lm(mpg ~ hp, data=mtcars)
kable(anova(fit))
```


# Figures.

\
The size of the figure in the document can best be controlled by setting dpi (dots per inch) and out.width (in number of pixels).

```{r, dpi=300, echo=FALSE, out.width="600px"}
par(mar=c(5,5,2,2))
palette(rainbow(3))
with(mtcars,plot(hp, mpg, pch=21, 
                 xlab="Horse power",
                 ylab="Miles per gallon",
                 bg=as.factor(gear), cex=1.2))
legend("topright", levels(as.factor(mtcars$gear)), pch=21, pt.bg=palette(),
       title="Gears")
```



